---
title: Talk of Talks
author: Talky Talker
date: Day of the Talk
---

```{r setup, include=F, cache=F}
library(knitr)
# attempt to set a reasonable code output textwidth
options(width=44)
opts_knit$set(width=44)
opts_chunk$set(
    comment=NA, # no comment chars decorating code output
    collapse=T, # multiple statements and output collapsed together
    dev="tikz", # TikZ graphs: nice but slow
    fig.width=4.5, fig.height=2.75,   # beamer cards are 128 mm x 96 mm
    size ='footnotesize',             # gets zoomed up to something reasonable
    dev.args=list(pointsize=9),
    message=F, warning=F,             # quit your chatter, R
    error=T,    # stop on error: can get annoying
    echo=F,     # hide chunk code by default
    cache=T,
    autodep=T)

# tikzDevice setup: install the tikzDevice package
options(tikzDefaultEngine="xetex")

# tikzDevice + xelatex
options(tikzXelatexPackages=c(
    "\\usepackage{tikz}\n",
    "\\usepackage[active,tightpage,xetex]{preview}\n",
    "\\usepackage{fontspec,xunicode}\n",
    "\\setmainfont{Gill Sans}\n",
    "\\PreviewEnvironment{pgfpicture}\n",
    "\\setlength\\PreviewBorder{0pt}\n"))

# load your favorite libraries
library(ggplot2)
library(xtable)

# import code from this file as chunks, to be included just below
read_chunk("slide-utils.R")
```

```{r code-hook, include=F, cache=F}
```

```{r plot-placement-hook, include=F, cache=F}
```

```{r dark-plot-theme, include=F}
```

```{r print-tabular, include=F}
```

# an example text slide


> - with an incremental
> - build

\note{<1>}{

And different notes on the first

}

\note{<2>}{

and second increments.

}

# an example table

```{r results="asis"}
print_tabular(mtcars[1:5, 1:5],
              floating=T,
              caption="Something about cars")
```

# an example graphic

```{r graph, fig.cap="I think that I shall never see"}
ggplot(trees, aes(Girth, Height)) +
    geom_point(color="white") +
    plot_theme()
```

# ugly examples of custom placement and sizing

```{r displaced, textblock_width=2.75, textblock_pos=c(0, 1), fig.height=3, fig.width=2, out.height=4, center=T}
p <- ggplot(mtcars, aes(factor(cyl))) +
    geom_bar(color="white", fill="grey40") +
    xlab("Another car thing") +
    plot_theme()
p
```

\begin{textblock}{2.75}(3,2)

Look! a dodgy three-column layout!

With great layout power comes great, etc., etc.
\end{textblock}

\begin{textblock}{2.75}(6,1)
```{r displaced-over, inside_textblock=T, center=T}
p
```

Text scaling: \\
a cautionary tale.
\end{textblock}

# example code display

```{r code, echo=T}
cor(anscombe$x1, anscombe$y1)
cor(anscombe$x2, anscombe$y2)
```

Definitely don't need to visualize.
